---
title: "Drake_Zhou_Part_04_B"
author: "Drake Zhou"
date: "4/26/2022"
output: 
  html_document: 
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview & Preparation

•You must identify which customers appear to be the hardest to predict in the regression and classification tasks.
•Base your conclusions on the best performing regression and classification models.
•You should base your conclusions on the resampled hold-out sets and NOT on the training set!
•Thus, save your hold-out set predictions!

## Package Import

```{r, message=FALSE}
library(caret)
library(yardstick)
library(tidyverse)
```

## Data Import

```{r, message=FALSE}
holdout <- readr::read_csv('final_project_holdout_inputs.csv', col_names = TRUE)
holdout_inputs <- holdout %>% 
  select(-rowid)

df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
# standard_df_all <- df_all %>%
#   select(starts_with("x"), region, customer) %>%
#   mutate(outcome = factor(df_all$outcome, levels = c("event", "non_event")),
#          region = df_all$region,
#          customer = df_all$customer)
df_all <- df_all %>%
  select(-rowid) %>%
  mutate(outcome = factor(outcome, levels = c("event", "non_event")))

# Resampling
train_id <- sample(1:nrow(df_all), size = floor(0.7 * nrow(df_all)))

train_ready <- df_all %>% slice(train_id)
test_ready <- df_all %>% slice(-train_id)
# test_ready <- df_all %>% slice(-train_id) %>% select(c(-response, -outcome, -rowid))

```

# Model

•You must identify which customers appear to be the hardest to predict in the regression and classification tasks.
•Base your conclusions on the best performing regression and classification models.
•You should base your conclusions on the resampled hold-out sets and NOT on the training set!
•Thus, save your hold-out set predictions!

## Model Import

```{r}
best_reg_mod <- readr::read_rds('models/fit_reg_enet_pair.rds')
best_cls_mod <- readr::read_rds('models/fit_acc_cat_nnet_tune.rds')
```

## Model Predict

### Regression model

```{r}
predict(best_reg_mod, test_ready) %>% head()
```

### Classification model

```{r}
predict(best_cls_mod, test_ready) %>% head()
```


# Interpretation

## Based on Train-set

### Function Preparation

```{r, eval=TRUE}
predict_df <- function(mod, test_data){
  my_preds <- tibble::tibble(
    y = predict(best_reg_mod, newdata = test_ready),
    pred_outcome = predict(best_cls_mod, newdata = test_ready)
  ) %>% 
  bind_cols(
    predict(best_cls_mod, newdata = test_ready, type = 'prob') %>% 
      select(probability = event)
  ) %>% 
  tibble::rowid_to_column('id')

  my_preds_all <- test_data %>%
    mutate(pred_response = my_preds$y,
           pred_outcome = factor(my_preds$pred_outcome, levels = c("event", "non_event")),
           pred_prob = my_preds$probability) %>%
    select(customer, response, pred_response, outcome, pred_outcome, pred_prob)
}

assess_mod <- function(my_preds_all){
  rmse_cal <- my_preds_all %>%
    group_by(customer) %>%
    rmse(estimate = pred_response, truth = response)
  
  mae_cal <- my_preds_all %>%
    group_by(customer) %>%
    mae(estimate = pred_response, truth = response)
  
  rsq_cal <- my_preds_all %>%
    group_by(customer) %>%
    rsq(estimate = pred_response, truth = response)
  
  acc_cal <- my_preds_all %>%
    group_by(customer) %>%
    accuracy(estimate = pred_outcome, truth = outcome)
  
  final_result <- tibble::tibble(
    customer = rmse_cal$customer,
    rmse = rmse_cal$.estimate,
    mae = mae_cal$.estimate,
    rsq = rsq_cal$.estimate,
    acc = acc_cal$.estimate
  )
}
```

```{r}
mod_df_all <- predict_df(best_reg_mod, test_ready)
mod_df <- mod_df_all %>% assess_mod()
mod_df
```

```{r}

mod_df %>%
  select(-acc) %>%
  pivot_longer(-c("customer")) %>%
  ggplot(mapping = aes(y = customer, x = value, group = 1))+
  geom_path()+
  geom_point(size = 2.0)+
  facet_grid(~name, scales = "free_x")+
  labs(x = '')+
  theme_bw()
```

According to figures above, in regression model, customer D and E are really hard to predict

```{r}
mod_df %>%
  select(acc, customer) %>%
  pivot_longer(-c("customer")) %>%
  ggplot(mapping = aes(y = customer, x = value, group = 1))+
  geom_linerange(mapping = aes(xmin = 0,
                               xmax = value)) +
  geom_point(size = 2.0)+
  labs(x = '')+
  theme_bw()
```

According to figures above, in regression model, customer Other and A are really hard to predict

## Based on Holdout-set

```{r}
my_preds <- tibble::tibble(
  customer = holdout_inputs$customer,
  y = predict(best_reg_mod, newdata = holdout_inputs),
  outcome = predict(best_cls_mod, newdata = holdout_inputs)
) %>% 
  bind_cols(
    predict(best_cls_mod, newdata = holdout_inputs, type = 'prob') %>% 
      select(probability = event)
  ) %>% 
  tibble::rowid_to_column('id')
```

```{r}
my_preds %>% 
  filter(customer == "A") %>%
  readr::write_csv('metric/my_predict_A.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "B") %>%
  readr::write_csv('metric/my_predict_B.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "D") %>%
  readr::write_csv('metric/my_predict_D.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "E") %>%
  readr::write_csv('metric/my_predict_E.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "G") %>%
  readr::write_csv('metric/my_predict_G.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "M") %>%
  readr::write_csv('metric/my_predict_M.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "Other") %>%
  readr::write_csv('metric/my_predict_Other.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "Q") %>%
  readr::write_csv('metric/my_predict_Q.csv', col_names = TRUE)
```

# Prediction Result Export 

```{r}
my_preds <- tibble::tibble(
  customer = holdout_inputs$customer,
  y = predict(best_reg_mod, newdata = holdout_inputs),
  outcome = predict(best_cls_mod, newdata = holdout_inputs)
) %>% 
  bind_cols(
    predict(best_cls_mod, newdata = holdout_inputs, type = 'prob') %>% 
      select(probability = event)
  ) %>% 
  tibble::rowid_to_column('id')
```

```{r}
my_preds %>% 
  filter(customer == "A") %>%
  readr::write_csv('metric/my_predict_A.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "B") %>%
  readr::write_csv('metric/my_predict_B.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "D") %>%
  readr::write_csv('metric/my_predict_D.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "E") %>%
  readr::write_csv('metric/my_predict_E.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "G") %>%
  readr::write_csv('metric/my_predict_G.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "M") %>%
  readr::write_csv('metric/my_predict_M.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "Other") %>%
  readr::write_csv('metric/my_predict_Other.csv', col_names = TRUE)
my_preds %>% 
  filter(customer == "Q") %>%
  readr::write_csv('metric/my_predict_Q.csv', col_names = TRUE)
```

