---
title: "Drake_Zhou_Part_03_D_03"
author: "Drake Zhou"
date: "4/26/2022"
output: 
  html_document: 
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview & Initialization

You must make predictions with your 2 selected generalized linear models in order to visualize the trends of the event probability with respect to the inputs.

## Package Import

```{r, init, message=FALSE}
library(tidyverse)
library(caret)
library(coefplot)
```

## Data Import

Before I fit into linear models, I want transform the response to log-response and standardized the inputs and outputs especially those continuous inputs.

```{r, eval=TRUE}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)

# Input standarize
standard_df_all <- df_all %>% 
  select(starts_with("x")) %>%
  mutate(obs = factor(df_all$outcome, levels = c("event", "non_event")),
         region = df_all$region, 
         customer = df_all$customer)

# Resampling
train_id <- sample(1:nrow(standard_df_all), size = floor(0.8 * nrow(standard_df_all)))
train_ready <- standard_df_all %>% slice(train_id)
test_ready <- standard_df_all %>% slice(-train_id)

```

# Import Model

## ROC

```{r}
fit_roc_cat_lm_add <- readr::read_rds('models/fit_roc_cat_lm_add.rds')
fit_roc_cat_lm_pair <- readr::read_rds('models/fit_roc_cat_lm_pair.rds')
fit_roc_cat_lm_mod1 <- readr::read_rds('models/fit_roc_cat_lm_mod1.rds')
fit_roc_cat_lm_mod2 <- readr::read_rds('models/fit_roc_cat_lm_mod2.rds')
fit_roc_cat_enet_pair <- readr::read_rds('models/fit_roc_cat_enet_pair.rds')
fit_roc_cat_enet_mod7 <- readr::read_rds('models/fit_roc_cat_enet_mod7.rds')
fit_roc_cat_enet_mod9 <- readr::read_rds('models/fit_roc_cat_enet_mod9.rds')
fit_roc_cat_gbm_warmup <- readr::read_rds('models/fit_roc_cat_gbm_warmup.rds')
fit_roc_cat_gbm_tune <- readr::read_rds('models/fit_roc_cat_gbm_tune.rds')
fit_roc_cat_nnet_warmup <- readr::read_rds('models/fit_roc_cat_nnet_warmup.rds')
fit_roc_cat_nnet_tune <- readr::read_rds('models/fit_roc_cat_nnet_tune.rds')
fit_roc_cat_rf_tune <- readr::read_rds('models/fit_roc_cat_rf_tune.rds')
fit_roc_cat_svm_tune <- readr::read_rds('models/fit_roc_cat_svm_tune.rds')
fit_roc_cat_cls_pls <- readr::read_rds('models/fit_roc_cat_cls_pls.rds')
```

## ROC Posterior Result

```{r}
roc_result <- resamples(list(LM_1 = fit_roc_cat_lm_add,
                                 #LM_2 = fit_roc_cat_lm_pair,
                                 LM_MOD1 = fit_roc_cat_lm_mod1,
                                 LM_MOD2 = fit_roc_cat_lm_mod2,
                                 ENET_PAIR = fit_roc_cat_enet_pair,
                                 ENET_MOD7 = fit_roc_cat_enet_mod7,
                                 ENET_MOD9 = fit_roc_cat_enet_mod9,
                                 GBM_W = fit_roc_cat_gbm_warmup,
                                 GBN_T = fit_roc_cat_gbm_tune,
                                 NNET_W = fit_roc_cat_nnet_warmup,
                                 NNET_T = fit_roc_cat_nnet_tune,
                                 RF = fit_roc_cat_rf_tune,
                                 SVM = fit_roc_cat_svm_tune,
                                 PLS = fit_roc_cat_cls_pls
                                 )
                            )
```

```{r}
dotplot(roc_result, scales = "free")
```

## Accuracy

```{r}
fit_acc_cat_lm_add <- readr::read_rds('models/fit_acc_cat_lm_add.rds')
fit_acc_cat_lm_pair <- readr::read_rds('models/fit_acc_cat_lm_pair.rds')
fit_acc_cat_lm_mod1 <- readr::read_rds('models/fit_acc_cat_lm_mod1.rds')
fit_acc_cat_lm_mod2 <- readr::read_rds('models/fit_acc_cat_lm_mod2.rds')
fit_acc_cat_enet_pair <- readr::read_rds('models/fit_acc_cat_enet_pair.rds')
fit_acc_cat_enet_mod7 <- readr::read_rds('models/fit_acc_cat_enet_mod7.rds')
fit_acc_cat_enet_mod9 <- readr::read_rds('models/fit_acc_cat_enet_mod9.rds')
fit_acc_cat_gbm_warmup <- readr::read_rds('models/fit_acc_cat_gbm_warmup.rds')
fit_acc_cat_gbm_tune <- readr::read_rds('models/fit_acc_cat_gbm_tune.rds')
fit_acc_cat_nnet_warmup <- readr::read_rds('models/fit_acc_cat_nnet_warmup.rds')
fit_acc_cat_nnet_tune <- readr::read_rds('models/fit_acc_cat_nnet_tune.rds')
fit_acc_cat_rf_tune <- readr::read_rds('models/fit_acc_cat_rf_tune.rds')
fit_acc_cat_svm_tune <- readr::read_rds('models/fit_acc_cat_svm_tune.rds')
fit_acc_cat_cls_pls <- readr::read_rds('models/fit_acc_cat_cls_pls.rds')
```

## Accuracy Posterior Result

```{r}
acc_result <- resamples(list(LM_1 = fit_acc_cat_lm_add,
                                 #LM_2 = fit_acc_cat_lm_pair,
                                 LM_MOD1 = fit_acc_cat_lm_mod1,
                                 LM_MOD2 = fit_acc_cat_lm_mod2,
                                 ENET_PAIR = fit_acc_cat_enet_pair,
                                 ENET_MOD7 = fit_acc_cat_enet_mod7,
                                 ENET_MOD9 = fit_acc_cat_enet_mod9,
                                 GBM_W = fit_acc_cat_gbm_warmup,
                                 GBN_T = fit_acc_cat_gbm_tune,
                                 NNET_W = fit_acc_cat_nnet_warmup,
                                 NNET_T = fit_acc_cat_nnet_tune,
                                 RF = fit_acc_cat_rf_tune,
                                 SVM = fit_acc_cat_svm_tune,
                                 PLS = fit_acc_cat_cls_pls
                                 )
                            )
```

```{r}
dotplot(acc_result, metric = "Accuracy")
```

Which model is the best if you are interested in maximizing Accuracy 
compared to maximizing the Area Under the ROC Curve (ROC AUC)?

```{text}
Accuracy and AUC curve provides different answer for which model is the best. According to Accuracy performance metric, tuned neural network is the best model while AUC prefers all pair-wise elastic net.

Best 2:
fit_roc_cat_enet_pair (pair is add)
fit_acc_cat_nnet_tune
```




