---
title: "Drake_Zhou_Part_04_A"
author: "Drake Zhou"
date: "4/26/2022"
output: 
  html_document: 
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview & Preparation

With the model training completed, you can now answer meaningful questions associated with the data!

## Package Import

```{r}
library(caret)
library(yardstick)
library(tidyverse)
```

• You must identify the best regression model and the best classification model.
• Identify the most important variables associated with your best performing models.

# Inspection

## Model Import

```{r}
best_reg_mod <- readr::read_rds('models/fit_reg_enet_pair.rds')
best_cls_mod <- readr::read_rds('models/fit_acc_cat_nnet_tune.rds')
```

## Variables Inspection

### Regression Model

```{r}
plot(varImp(best_reg_mod), top = 20)
```

### Classification Model

```{r}
plot(varImp(best_cls_mod), top = 20)
```

• Are the most important variables similar for the regression and classification tasks?

```{text}
No, they are not similar
```

• Does one of the sentiment derived feature types “dominate” the most important variables?

```{text}
In regression model, even though we are using all pair-wise models, most of important features are interaction between two factors, but we see that "xw" and sentiment appears a lot of time. 
In classification model, we see a lot of xn and xa
```

• Does one of the sentiment derived feature types appear to be not helpful at all?

```{text}
Don't really see a helpless features set. But xb sentiment derived features seem appear very less. If there has to be one "no help" sentiment feature, it could be xs.
```

• Based on your modeling results, do you feel these sentiment derived features are helpful at predicting the outputs? 

```{text}
Yes, it is a very important input.
```

• Essentially, do you feel the model results are “good” and was I right about the relationship between report sentiment and the outputs?

```{text}
Yes, generally speaking, sentiment and output have strong relationship
```

