---
title: "Drake_Zhou_Part_02_C"
author: "Drake Zhou"
date: "4/25/2022"
output: 
  html_document: 
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview & Preparation

## Package Import

This part is mainly focus on making prediction, I will import top 2 Bayesian models and then make predictions. Then test the impact of different variables, and evluate the model. Finally I will select the best model.

```{r, init, message=FALSE}
library(tidyverse)
library(caret)
library(coefplot)
library(rstanarm)
library(splines)
```

## Data Import

```{r}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
df_all <- df_all %>% 
  mutate(y = log(response)) %>% 
  select(region, customer, starts_with('x'), y)
```
# Predictive Trends

## Input grid prepare

The make_test_input_list() function therefore creates a grid of 25 evenly spaced points between the training set min and max bounds for the top 2 ranked inputs. The third and fourth ranked inputs are given 5 unique values, based on specific quantiles of the training set. All other inputs are set to constant values equal to their training set medians.

```{r, make_input_grid_01, eval=TRUE}
make_test_input_list <- function(var_name, top_4_inputs, all_data)
{
  xvar <- all_data %>% select(all_of(var_name)) %>% pull()
  
  if (var_name %in% top_4_inputs[1]){
    # use 25 unique values between the min/max values
    xgrid <- seq(min(xvar), max(xvar), length.out = 25)
  } else if (var_name %in% top_4_inputs[2]){
    # specify quantiles to use
    xgrid <- quantile(xvar, probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = TRUE)
    xgrid <- as.vector(xgrid)
  } else {
    # set to their median values
    xgrid <- median(xvar, na.rm = TRUE)
  }
  
  return(xgrid)
}
```

The second function, make_test_input_grid(), is a wrapper function. It iteratively applies the make_test_input_list() function to all inputs and then uses the expand.grid() function to create full factorial grid based on the list of unique input values.

```{r, make_input_grid_02, eval=TRUE}
make_test_input_grid <- function(all_input_names, top_4_inputs, all_data)
{
  test_list <- purrr::map(all_input_names, 
                          make_test_input_list,
                          top_4_inputs = top_4_inputs,
                          all_data = all_data)
  
  expand.grid(test_list, 
              KEEP.OUT.ATTRS = FALSE,
              stringsAsFactors = FALSE) %>% 
    purrr::set_names(all_input_names)
}
```

Manually select the top 4 inputs

```{r, make_input_grid_03, eval=TRUE}
my_input_names <- df_all %>% dplyr::select(-y) %>% names()
my_top_ranked_inputs <- c("xb_04","xw_01")
viz_input_grid <- make_test_input_grid(my_input_names, my_top_ranked_inputs, df_all)
```

## Import models

```{r, message=FALSE}
rstanarm_mod3 <- readr::read_rds('models/rstanarm_mod3.rds')
rstanarm_mod9 <- readr::read_rds('models/rstanarm_mod9.rds')
```

## Model 3

```{r}
post_pred_mod3 <- posterior_predict(rstanarm_mod3, newdata = viz_input_grid)
```

```{r}
post_pred_mod3 %>%
  as.data.frame() %>% tibble::as_tibble() %>%
  tibble::rowid_to_column("post_id") %>%
  tidyr::gather(key = "pred_id", value = "value", -post_id) %>%
  mutate_at(c("pred_id"), as.numeric) %>%
  group_by(pred_id) %>%
  summarise(num_post = n(),
            trend_avg = mean(value),
            trend_lwr = quantile(value, 0.05),
            trend_upr = quantile(value, 0.95)) %>%
  ungroup() %>%
  left_join(viz_input_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>%
  ggplot(mapping = aes(x = xb_04)) +
  geom_ribbon(mapping = aes(ymin = trend_lwr,
                            ymax = trend_upr,
                            group = xw_01,
                            fill = as.factor(xw_01)),
              alpha = 0.5) +
  geom_line(mapping = aes(y = trend_avg,
                          group = xw_01,
                          color = as.factor(xw_01)),
            size = 1.) +
  scale_fill_viridis_d("xw_01") +
  scale_color_viridis_d("xw_01") +
  labs(y = "mean trend") +
  theme_bw() +
  theme(legend.position = "top")
```


```{r}
post_pred_mod3 %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  tidyr::gather(key = "pred_id", value = "value", -post_id) %>% 
  mutate_at(c("pred_id"), as.numeric) %>% 
  group_by(pred_id) %>% 
  summarise(y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(posterior_linpred(rstanarm_mod3, newdata = viz_input_grid) %>% 
              as.data.frame() %>% tibble::as_tibble() %>% 
              tibble::rowid_to_column("post_id") %>% 
              tidyr::gather(key = "pred_id", value = "value", -post_id) %>% 
              mutate_at(c("pred_id"), as.numeric) %>% 
              group_by(pred_id) %>% 
              summarise(trend_avg = mean(value),
                        trend_lwr = quantile(value, 0.05),
                        trend_upr = quantile(value, 0.95)) %>% 
              ungroup(),
            by = "pred_id") %>% 
  left_join(viz_input_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = xb_04)) +
  geom_ribbon(mapping = aes(ymin = y_lwr, ymax = y_upr,
                            group = xw_01), 
              fill = "darkorange") +
  geom_ribbon(mapping = aes(ymin = trend_lwr, ymax = trend_upr,
                            group = xw_01),
              fill = "grey") +
  geom_line(mapping = aes(y = trend_avg,
                          group = xw_01),
            color = "black", size = 0.85) +
  facet_wrap(~xw_01, labeller = "label_both", scales = 'free') +
  labs(y = "y") +
  theme_bw()
```

```{r}
posterior_predict(rstanarm_mod3, newdata = viz_input_grid) %>%
  as.data.frame() %>% tibble::as_tibble() %>%
  tibble::rowid_to_column("post_id") %>%
  tidyr::gather(key = "pred_id", value = "value", -post_id) %>%
  mutate_at(c("pred_id"), as.numeric) %>%
  group_by(pred_id) %>%
  summarise(num_post = n(),
            y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95),
            prob_grt_0 = mean(value > 0)) %>%
  ungroup() %>%
  left_join(viz_input_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>%
  ggplot(mapping = aes(x = xb_04, y = prob_grt_0)) +
  geom_line(mapping = aes(group = xw_01,
                          color = as.factor(xw_01)),
            size = 1.) +
  scale_fill_viridis_d("xw_01") +
  scale_color_viridis_d("xw_01") +
  labs(y = "Probability response is greater than 0") +
  theme_bw() +
  theme(legend.position = "top")
```

## Model 9

```{r}
posterior_predict(rstanarm_mod9, newdata = viz_input_grid) %>% dim()
```

```{r}
posterior_predict(rstanarm_mod9, newdata = viz_input_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  tidyr::gather(key = "pred_id", value = "value", -post_id) %>% 
  mutate_at(c("pred_id"), as.numeric) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            trend_avg = mean(value),
            trend_lwr = quantile(value, 0.05),
            trend_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(viz_input_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = xb_04)) +
  geom_ribbon(mapping = aes(ymin = trend_lwr,
                            ymax = trend_upr,
                            group = xw_01,
                            fill = as.factor(xw_01)),
              alpha = 0.5) +
  geom_line(mapping = aes(y = trend_avg,
                          group = xw_01,
                          color = as.factor(xw_01)),
            size = 1.) +
  scale_fill_viridis_d("xw_01") +
  scale_color_viridis_d("xw_01") +
  labs(y = "mean trend") +
  theme_bw() +
  theme(legend.position = "top")
```


```{r}
posterior_predict(rstanarm_mod9, newdata = viz_input_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  tidyr::gather(key = "pred_id", value = "value", -post_id) %>% 
  mutate_at(c("pred_id"), as.numeric) %>% 
  group_by(pred_id) %>% 
  summarise(y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(posterior_linpred(rstanarm_mod9, newdata = viz_input_grid) %>% 
              as.data.frame() %>% tibble::as_tibble() %>% 
              tibble::rowid_to_column("post_id") %>% 
              tidyr::gather(key = "pred_id", value = "value", -post_id) %>% 
              mutate_at(c("pred_id"), as.numeric) %>% 
              group_by(pred_id) %>% 
              summarise(trend_avg = mean(value),
                        trend_lwr = quantile(value, 0.05),
                        trend_upr = quantile(value, 0.95)) %>% 
              ungroup(),
            by = "pred_id") %>% 
  left_join(viz_input_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = xb_04)) +
  geom_ribbon(mapping = aes(ymin = y_lwr, ymax = y_upr,
                            group = xw_01), 
              fill = "darkorange") +
  geom_ribbon(mapping = aes(ymin = trend_lwr, ymax = trend_upr,
                            group = xw_01),
              fill = "grey") +
  geom_line(mapping = aes(y = trend_avg,
                          group = xw_01),
            color = "black", size = 0.85) +
  facet_wrap(~xw_01, labeller = "label_both", scales = 'free') +
  labs(y = "y") +
  theme_bw()
```

```{r}
posterior_predict(rstanarm_mod9, newdata = viz_input_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  tidyr::gather(key = "pred_id", value = "value", -post_id) %>% 
  mutate_at(c("pred_id"), as.numeric) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95),
            prob_grt_0 = mean(value > 0)) %>% 
  ungroup() %>% 
  left_join(viz_input_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = xb_04, y = prob_grt_0)) +
  geom_line(mapping = aes(group = xw_01,
                          color = as.factor(xw_01)),
            size = 1.) +
  scale_fill_viridis_d("xw_01") +
  scale_color_viridis_d("xw_01") +
  labs(y = "Probability response is greater than 0") +
  theme_bw() +
  theme(legend.position = "top")
```

# Conclusion

```{text}
Clearly, they are not consistent with each other.
```
